---
title: "index.Rmd"
author: "Julio Lopez"
date: "`r Sys.Date()`"
output: 
  html_document: 
    highlight: pygments
    theme: cerulean
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## pa3
1. Load the dataset of your choice and get information about its structure
```{r}
library(tidyverse)
library(languageR)

str(selfPacedReadingHeid)
# I have loaded the dataset I am going to work with.
# I have looked at its structure
```
2. Tidy the dataset (every variable gets a column, every observation occupies a single row), if necessary.
```{r}
str(selfPacedReadingHeid)
my_data <- selfPacedReadingHeid %>%
  select(., x = RT1WordLater, y = RT)
# The dataset seems to be tidied.
# I have created a new dataset with the variables I am interested in.
```
3. Calculate descriptive statistics of your choice.
```{r}
my_data %>%
  ggplot(., aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  labs(x = 'Reaction Time in Following Word', y = 'Reaction Time in -Heid word')

# I have made a scatterplot using the two variables and set lm through the data.
```
The mean reaction time for -Heid word was `r mean(my_data$y)`, with a standard deviation of `r sd(my_data$y)`. The median was `r median(my_data$y)`.
On the other hand, the mean reaction time for the word following the -Heid words was `r mean(my_data$x)`, with a standard deviation of `r median(my_data$x)`, while the median was `r sd(my_data$x)`.

4. Select two continuous variables and fit a model to the data (bivariate regression).
```{r}
myfit <- lm(x ~ y, data = my_data)
summary(myfit)
# I had already selected my variables before.
```
5. Generate a plot that includes a regression line.
```{r}
my_data %>%
  ggplot(., aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  labs(x = 'Reaction Time in Following Word', y = 'Reaction Time in -Heid word')
# I had already created this plot above; plots help me visualize the data.
```
6. Write up some general observations (1-2 paragraphs max)

The linear model fit in the data shows that there exists a positive correlation between y (Reaction Time in the -Heid Word) and x (Reaction Time in Word Following the -Heid Word). Specifically, as Y increases in one unit, X increases in 0.21274 units.

However, the multiple R-squared is 0.07445 and the adjusted R-squared is 0.07373. According to Lewis-Beck, a value over .90 is necessary for the results to be trustwhorty in the hard sciences and .30 in the social sciences. Therefore, our results are not reliable: Reaction Time in -Heid Words are not a predictor for Reaction Time in the Following Word.
